---
title: "p8105_hw2_jy2965"
author: "Jun"
date: "9/28/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(tidyr)
```

## Problem 1

# read and clean data
**Mr. Trash Wheel sheet**
```{r}
trash_data = read_excel("./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx","Mr. Trash Wheel", range = "A2:N408" )  %>% 
  janitor::clean_names() %>% 
  rename(weight= weight_tons, volume = volume_cubic_yards) %>% 
  drop_na(dumpster) %>% 
  mutate(
    sports_balls = round(sports_balls, digits = 0),
    sports_balls = as.integer(sports_balls)
)
```
In above chunck, I managed to do:
1.specify the sheet in the Excel file and to omit non-data entries (rows with notes / figures; columns containing notes) using arguments in read_excel
2.use reasonable variable names
3.omit rows that do not include dumpster-specific data
4.round the number of sports balls to the nearest integer and converts the result to an integer variable (using as.integer)

