---
title: "p8105_hw2_jy2965"
author: "Jun"
date: "9/28/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(tidyr)
```

## Problem 1

# read and clean data
**Mr. Trash Wheel sheet**
```{r}
trash_data = read_excel("./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx","Mr. Trash Wheel", range = "A2:N408" )  %>% 
  janitor::clean_names() %>% 
  rename(weight= weight_tons, volume = volume_cubic_yards) %>% 
  drop_na(dumpster) %>% 
  mutate(
    sports_balls = round(sports_balls, digits = 0),
    sports_balls = as.integer(sports_balls)
)
```
In above chunk, I managed to do:
1.specify the sheet in the Excel file and to omit non-data entries (rows with notes / figures; columns containing notes) using arguments in read_excel
2.use reasonable variable names
3.omit rows that do not include dumpster-specific data
4.round the number of sports balls to the nearest integer and converts the result to an integer variable (using as.integer)

**data for 2017 and 2018**
```{r}
precipitation_2017 = read_excel("./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx","2017 Precipitation", range = "A2:B14" )  %>% 
  janitor::clean_names() %>% 
  mutate(
   year = 2017
)
precipitation_2018 = read_excel("./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx","2018 Precipitation", range = "A2:B14" )  %>% 
  janitor::clean_names() %>% 
  mutate(
   year = 2018
)

combine_precipitation = bind_rows(precipitation_2017,precipitation_2018) %>% 
  janitor::clean_names() %>% 
  mutate(month = month.name[month]) %>% 
  select(year, everything())
```

The dataset "trash_data" contains the data from the first sheet of the "Trash-Wheel-Collection-Totals-8-6-19.xlsx" file. This data has `r nrow(trash_data)` rows, `r ncol(trash_data)` columns and `r nrow(trash_data)` observations. Besides, this dataset has `r ncol(trash_data)` variables. Taking "weight" as an example, dumpster1 collected 4.31 tons of trash on May 16th, 2014.

The dataset "combine_precipitation" combines the data from "2017 precipitation" and "2018 preciptation" sheet of the "Trash-Wheel-Collection-Totals-8-6-19.xlsx" file. This data has `r nrow(combine_precipitation)` rows, `r ncol(combine_precipitation)` colums and `r nrow(combine_precipitation)` observations. Besides, this dataset has `r ncol(combine_precipitation)` variables. For example, the total precipetation in January 2017 is 2.34.
**answer the question**
For available data, what was the total precipitation in 2018? What was the median number of sports balls in a dumpster in 2017?
The total precipitation in 2018 is `r sum(precipitation_2017$total)`.
The median number of sports balls in a dumpster in 2017 is `r median(filter(trash_data, year == "2017")$sports_balls)`

## Problem 2
**data in pols-month.csv**
```{r}
pols_month = read_csv(file = "./data/pols-month.csv") %>% 
  janitor::clean_names() %>% 
  separate(mon, into = c("year", "month", "day"), sep = "-") %>% 
  mutate(month = month.name[as.integer(month)],
         president = prez_gop+prez_dem
         ) %>% 
  select(-prez_dem,-prez_gop,-day)
```
**data in snp.csv**
```{r}
snp_data = read_csv(file = "./data/snp.csv") %>% 
  janitor::clean_names() %>% 
  separate(date, into = c("day", "month", "year"), sep = "/") %>% 
  mutate(month = month.name[as.integer(month)]) %>% 
  select(year, month, close)
```
**unemployment data**
```{r}
unemployment_data = read_csv(file = "./data/unemployment.csv") %>% 
  janitor::clean_names() %>% 
  rename(January = jan, February = feb, March = mar, April = apr, 
         May = may, June = jun, July = jul, August = aug, September=sep, October = oct, November = nov, December = dec) %>% 
  pivot_longer(January:December, names_to = "month", values_to = "unemployment")
```
**merge variables**
```{r}
merge_data_test = left_join(pols_month,snp_data, by = c("year","month"))
```


